I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-08 Paper/Paper_noProof.tex

@@

We explain the framework in 4 subsections: precomputation, process for one image, process for one node, and global process.

@@

@@

@@

The following table is the summary of 5 experiments.

@@

We compare our method to two famous verifiers (their incomplete mode): PRIMA and $\beta$-Crown on 5 typical MNIST models. Basically, our method can exceed PRIMA on both accuracy and speed, and exceed $\beta$-Crown on accuracy.

We do tests on 5 typical MNIST models.

>>>>

And the pseudo-code is as follows:

\begin{algorithm}
	\caption{Process for length 3 + length 4}
	\KwData{Sorted lists of length 3 + length 4}
	\KwResult{Open node list}

	Let $N = 0$ be the number of Chosen length 4 pair.

	\While{len(Open node) $<O$}{
		Pick the first element $P_3$ in the list of length 3\;

		Let $V_3$ be the value of $P_3$\;

		Pick the first element $P_4$ in the list of length 4\;

		Let $V_4$ be the value of $P_4$\;

		\If{$V_3 > V_4 \cdot N$}{
			Add nodes in $P_3$ into Open list\;
			Number of Chosen lentgh pair $N$ += 1\; 
		}
		\Else{
			Add nodes in $P_4$ into Open list\;
		}
	}
\end{algorithm}

@@

In this section, We will explain our framework in 4 subsections: precomputation, process for one image, process for one node, and global process.

@@

\begin{table}
	\centering
	\begin{tabular}{c|c|c}

	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
	0  &  2.22 & 2.22  \\ \hline
	10  &  1.84 & 2.03  \\ \hline
	20  &  1.50 & 1.82  \\ \hline
	30  &  1.28 & 1.62  \\ \hline
	40  &  1.14 & 1.44  \\ \hline
	50  &  1.06 & 1.23  \\ \hline
\end{tabular}
\caption{}
\label{tab:example0}
\end{table}

@@

\begin{table}
	\centering
	\begin{tabular}{c|c|c}

	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
	0  &  1.758 & 1.758  \\ \hline
	10  &  1.677 & 1.695  \\ \hline
	20  &  1.539 & 1.622  \\ \hline
	30  &  1.431 & 1.542  \\ \hline
	40  &  1.329 & 1.47  \\ \hline
	50  &  1.243 & 1.39  \\ \hline
\end{tabular}
\caption{}
\label{tab:example1}
\end{table}

@@

@@

In Table 3, we compare against two representative incomplete
verifiers on 4 MLP networks for MNIST under the same
set of 1000 images. beta-Crown is the state-of-the-art verifier based on branch-and-bound. PRIMA is another strong and representative method based on multi-neuron linear relaxation.

\begin{table}
	\centering
	\begin{tabular}{c|c|cc|cc|cc|cc}

		\text{Network}  & $\varepsilon$&  \multicolumn{2}{@{}c@{}|}{\text{Comp(fast)}} & \multicolumn{2}{@{}c@{}|}{\text{PRIMA}} &  \multicolumn{2}{@{}c@{}|}{\text{Comp(slow)}} & \multicolumn{2}{@{}c@{}|}{\text{beta-Crown}}  \\

		&  & \textrm{Ver}.\% & \textrm{Time}(s) & \textrm{Ver}.\% & \textrm{Time}(s) &\textrm{Ver}.\% & \textrm{Time}(s) & \textrm{Ver}.\% & \textrm{Time}(s) \\ \hline

		\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

		\textrm{MLP}\ 8$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

		\textrm{MLP}\ 5$\times$200\  &   0.015& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

		\textrm{MLP}\ 8$\times$200\  &   0.015& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

		\textrm{MLP}\ 6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
	\end{tabular}
	\caption{The data of verified accuracy (\%) and average time (s) of 1000 images evaluated on the PRIMA and on the beta-Crown are in CITE.}
	\label{tab:example}
\end{table}

On all 4 networks, our fast version can exceed PRIMA both in accuracy and speed. On all 4 networks, our slow version can have a similar verified accuracy as beta-Crown.
